---
title: "Weather Preferences in the United States"
subtitle: "Summary REport for the `r params$region`Region"
author: "Monica Cortinas"
date: "`r format(Sys.Date(), '%A, %B %d, %Y')`"
output: html_document
params:
  region: 
    label: "Region:"
    value: Mountain
    input: select
    choices: ["East North Central","East South Central", "Middle Atlantic","Mountain", "New England", "Pacific","South Atlantic", "West North Central", "West South Central"]
---

```{r setup, include=FALSE}

# define knitr options

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

# set any missing NAs in tables to blank
options(knitr.kable.NA='')

# load R packages
library(fivethirtyeight)
library(tidyverse)
library(fivethirtyeight)
library(knitr)
library(kableExtra)
library(ggthemes)

# load weather dataset

data("weather_check", package="fivethirtyeight")

# create subset no missing NAs
# pick a specific region
sdat <- weather_check %>%
      filter(region=="Mountain")
```

## Background

In May 2014, Walt Hickey at
[538.com](http://fivethirtyeight.com/) published an
article entitled
["How Americans Like Their Steak"](https://fivethirtyeight.com/features/how-americans-like-their-steak/). This article utilized survey data collected from 550 people which asked questions related to various risky activities, such as whether they speed in traffic, if they smoke or go skydiving, and if they prefer a riskier lottery. The survey also asked if they eat steak and if so, how they prefer their steak.


## Purpose

The "steak survey" dataset that was used for the ["How
Americans Like Their
Steak"](https://fivethirtyeight.com/features/how-americans-like-their-steak/) article, is available through
the R package [`fivethirtyeight`](https://cran.r-
project.org/web/packages/fivethirtyeight/index.html).
Using this dataset, this article summarizes the steak
preferences for the _**Mountain**_ Region of the
United States by gender.

For our summary presented here, a subset of the original steak survey was extracted to only include responses with no missing data and only included respondents from the _**Mountain**_ region of the US. The data subset used for our summary had `r nrow(sdat)` respondents.



## Weather Source Preference by Gender

Finally, here is a breakdown of the `r nrow(sdat)` survey respondents for the `r params$region` region of the US on how they check their daily weather by gender.

```{r}
library(stringr)
ggplot(sdat, 
       aes(x = weather_source, fill = female)) + 
  geom_bar(position="dodge",colour="black") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  ggtitle(paste0("Weather Source by Gender: ",
                 params$region," Region")) +
  xlab("Weather Source Preference") +
  ylab("Number of Respondents") +
  scale_fill_manual(values=c("skyblue","palevioletred"),
    name="Gender",
    breaks=c(FALSE,TRUE),
    labels=c("Male", "Female")) +
  coord_flip() +
  theme_fivethirtyeight()
```
